\documentclass[12pt]{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\ScrumBot}
\author{
	Team 304, ScrumBot
		\\ Arkin Modi, modia1
        \\ Leon So, sol4
        \\ Timothy Choy, choyt2
}
\date{Last Updated: January 23, 2020}

\begin{document}

\begin{table}[hp]
    \caption{Revision History} \label{TblRevisionHistory}
    \begin{tabularx}{\textwidth}{llX}
        \toprule
            \textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
        \midrule
            January 20, 2020 & Leon So & Copy template, rough draft\\
            January 23, 2020 & Everyone & Update problem statement\\
            January 23, 2020 & Everyone & Add stakeholders and headings\\
        \bottomrule
    \end{tabularx}
\end{table}

\newpage
\maketitle

\section{Problem Statement}
Scrum is an agile process framework widely used in industry for managing and coordinating collaborative projects. Scrum being a process based on the agile development method, follows a highly iterative process and often has heavy customer involvement, therefore it can be often be complex. It is often difficult to manage communication and coordination within the project due to the complexity of agile development processes. With Discord being a popular communication tool used by many teams of software developers today, our team would like to develop a solution to directly integrate the management of a scrum development cycle into the communication channels. Our solution will allow for better management and organization of retrospectives, stand-ups, and other scrum/agile processes used by software teams during routine communication.\\

As a result, a well-integrated scrum management system may reduce inefficiencies surrounding the management of projects using the scrum framework, as well as strengthen communication within the agile process. This will help software development firms reduce costs and achieve better workflow. Therefore, all members of the development and management team will be able to benefit from a scrum management system that is directly integrated into the communication channel.

\section{Stakeholders}
This solution will be used in an environment where the development team uses the scrum agile framework and uses Discord as their routine communication channel.
\begin{itemize}
  \item Roles in Scrum process:
  \begin{itemize}
    \item Product Owner(s)
    \begin{itemize}
      \item[] The product owner(s) will benefit from the reduced development time through improved communication and efficient management of the project. The product owner(s) will also benefit as their ideas and requirements will be better organized, thus helping the development team more efficiently achieve the goals of the product owner(s).
    \end{itemize}
    \item Scrum Master
    \begin{itemize}
      \item[] The scrum master will be better able to coordinate scrum plans and division of tasks, as well as routine communication (i.e. retrospectives and stand-ups). With a scrum management system directly implemented into the communication channels, the scrum master will be able to directly manage the meeting information and their scrum development cycle during communication.
    \end{itemize}
    \item Development Team
    \begin{itemize}
      \item[] The development team will be able to more easily follow through on tasks assigned by the scrum master. The development team may easily refer to any relevant articles or information regarding their project. This will reduce inefficiencies and speedup communication within the development team. It will also reduce confusion, as all information concerning the development cycle will be available through their routine communication channel (Discord).
    \end{itemize}
  \end{itemize}
  \item Other stakeholders:
  \begin{itemize}
    \item Development Firm
    \begin{itemize}
      \item[] The development firm will benefit through centralizing project resources, therefore improving the organization and management of the project. The development firm will therefore be able to reduce any costs associated with inefficiencies during the development process. This will also improve communication between members of the development firm.
    \end{itemize}
  \end{itemize}
\end{itemize}
\end{document}